Mining Interaction Log Data in a Creative Arts Practice using Transition Matrices

### 2015-09-24 flux-entropy-paper/flux-entropy-paper.tex
minor adjustment

In all of our 95 interaction sessions, every touch interaction---
touches begin, touches move, touches end ---was time-stamped and
logged to disk for later analysis. These sessions included {\em rehearsals} without an
audience, as well as {\em concerts}, in front of a live audience, where 
performative goals were paramount. They also included a number of {\em
  recording} sessions
for the purposes of formally-structured HCI experiments. In the recording
sessions, the performers were also interviewed and surveyed-- something which would have 
been disruptive and inappropriate for the concerts. Survey and interview data were not part of the
corpus. 
Some of the sessions were
iPad-only and others used iPads together with other acoustic
percussion instruments. Although the majority of the sessions were
free-form improvisations, a number of rehearsals and performances
involved composed pieces where the musicians read and performed
percussion notation using the apps.
Some of these session contexts are are shown
Figure~\ref{fig:three-performance-contexts} and other descriptive
statistics about the corpus are shown in Table \ref{corpus-table}.
In our corpus, the median length of sessions is 7m26s and the median
number of participants per ensemble is four. Each session record is
labelled with metadata about its \emph{context} (concert,
rehearsal, recording), its \emph{type} (improvisation or composition),
and its \emph{instrumentation} (iPads-only, or iPads with acoustic
percussion). The distribution of recorded sessions by context and type
is shown in Figure \ref{fig:count-data}.

>>>>

In all of our 95 interaction sessions, every touch interaction 
(touches begin, touches move, touches end) was time-stamped and
logged to disk for later analysis. These sessions included {\em rehearsals} without an
audience, as well as {\em concerts}, in front of a live audience, where 
performative goals were paramount. They also included a number of {\em
  recording} sessions
for the purposes of formally-structured HCI experiments. In the recording
sessions, the performers were also interviewed and surveyed-- something which would have 
been disruptive and inappropriate for the concerts. Survey and interview data were not part of the
corpus. 
Some of the sessions were
iPad-only and others used iPads together with other acoustic
percussion instruments. Although the majority of the sessions were
free-form improvisations, a number of rehearsals and performances
involved composed pieces where the musicians read and performed
percussion notation using the apps.
Some of these session contexts are are shown
Figure~\ref{fig:three-performance-contexts} and other descriptive
statistics about the corpus are shown in Table \ref{corpus-table}.
In our corpus, the median length of sessions is 7m26s and the median
number of participants per ensemble is four. Each session record is
labelled with metadata about its \emph{context} (concert,
rehearsal, recording), its \emph{type} (improvisation or composition),
and its \emph{instrumentation} (iPads-only, or iPads with acoustic
percussion). The distribution of recorded sessions by context and type
is shown in Figure \ref{fig:count-data}.
